Exception Handling Bug Hazards in Android

### 2015-09-28 SPRINGER_JOURNAL/msr_journal.tex
RQ1 e RQ2

Our main goal is to learn from developers perspective about the main exception handling bug hazards in Android. We therefore use a survey as our main research instrument. The survey mixed  Liket-scale with open-ended questions. The questions were motivated by the analysis of the existing bug hazards detected in the first phase of this study. Next sections detail the survey.

@@

@@

 In previous work~\cite{co15}, we mined exception stack traces available on issues reported on several Android projects hosted in GitHub and Googlecode. To ensure that our sample consists of repositories that were real Android apps, we had to inspect every project site and discard the toy-programs and non-Android repositories. For each repository, we extract the developers whose email are registered on each repository. We emailed the developers and received 74 answers.

@@

Developers were also asked whether the exception handling code helped with the development of robust Android applications. Although most of the developers answered positively (78.9\%) when asked to provide one or more reasons for their answers, most of them said that if not carefully developed the exception handling code may lead to app crashes. Table XXX presents the top reasons why the exception handling code may or may not help de development of robust apps.

\begin{table}
\scriptsize
\centering
\begin{tabular}{lrr}
\hline
\bfseries{Top 5 Resons} & \bfseries{\#} & \bfseries{\%} \\
\hline
\bfseries{For Positively Affecting Robustness} &   &   \\
Programming logic (java.lang and util)  & 52,0\% & 52,0\%\\
Resources (IO, Memory, Batery)  & 52,0\% & 23,9\% \\
Security  & 52,0\% & 4,1\%\\
Concurrency  & 52,0\% & 2,9\% \\
Backward compatibility  & 52,0\% & 5,5\% \\
\bfseries{For Negatively Affecting Robustness} &   &   \\
Specific Exceptions  & 52,0\% & 4,9\%\\
General (Error, Exception, Runtime)  & 52,0\% & 6,7\%\\
Specific Exceptions  & 52,0\% & 4,9\%\\
General (Error, Exception, Runtime)  & 52,0\% & 6,7\%\\
\hline
\end{tabular}
\caption{Top 5 reasons why exception handling helps or impairs the development of robust apps}
\label{tab:tophundrend}
\end{table}

>>>>

Our main goal is to learn from developers perspective about the Java exception handling usage and the main exception handling bug hazards in Android. We therefore use a survey as our main research instrument. The survey mixed  Liket-scale with open-ended questions. The questions were motivated by the analysis of the existing bug hazards detected in the first phase of this study. Next sections detail the survey.

@@

We used grounded theory coding~\cite{charmaz2006}, iterating through our open-ended survey responses, to answer some of the research questions. The grounded theory coding used in this study consists of at two phases: (1) initial coding entails a close reading of the data and (2) later we use focused coding ~\cite{charmaz2006} to pinpoint and develop the most salient themes~\cite{charmaz2006} in the analyzed data.

@@

 In previous work~\cite{coelhoetal15}, we mined exception stack traces available on issues reported on several Android projects hosted in GitHub and Googlecode. To ensure that our sample consists of repositories that were real Android apps, we had to inspect every project site and discard the toy-programs and non-Android repositories. For each repository, we extract the developers whose email are registered on each repository. We emailed the developers and received 74 answers.

@@

Developers were also asked whether the exception handling code helped with the development of robust Android applications. Although most of the developers answered positively (78.9\%) when asked to provide one or more reasons for their answers, most of the respondents also provide reasons why the exception handling code can sometimes impairs the robustness.  Since positive and negative reasons were provided intermixed we analyzed both set of answers and ranked the top reasons why exception handling that can negatively or positively affect robustness according to developers perceptions.

 Table ~\ref{tab:topreasons} presents the top reasons why the exception handling code may or may not help de development of robust apps. Although most of the respondents answered that exception handling code helped with the development of robust Android applications, almost every respondent pointed a drawback associated to he exception handling code, saying that if not used with care the exception handling code may lead to app crashes.

\begin{table}
\scriptsize
\centering
\begin{tabular}{lrr}
\hline
\bfseries{Top Resons} & \bfseries{\#} & \bfseries{\%} \\
\hline
\bfseries{For Positively Affecting Robustness} &   &   \\
Exception message improves error diagnosis &	10	& 14\% \\
Anticipated erroneous situation help writing more robust code & 9	 & 13\% \\
Exceptions for unrecoverable behavior	& 7 &	10\% \\
Checked exceptions force handling  &	6	& 9\% \\
Useful to gracefully crash 	& 4 &	6\% \\

\bfseries{For Negatively Affecting Robustness} &   &   \\
Exceptions should be caught to improve robustness	& 7	& 10\% \\
Creates a different control flow makes debugging harder &	2 &	3\% \\
unchecked/runtime exceptions favor crashes	& 2	& 3\% \\
NullPointerExceptoins are tricky to avoid	 & 2	& 3\% \\
Many device specific exceptions prevent proper handling	& 1 & 1\% \\

\hline
\end{tabular}
\caption{Top 5 reasons why exception handling helps or impairs the development of robust apps}
\label{tab:topreasons}
\end{table}
